---
title: "Golf-Ball-Project"
author: "Abhay Kulkarni"
date: "26/06/2019"
output:
  github_document:
    toc: true
    toc_depth: 2
  html_document:
   fig_caption: yes
   pdf_document: default
   number_sections: yes
   df_print: paged
   toc: yes
   toc_depth: '1'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

```
  
\newpage


# Introduction   
   
" Par Inc., is a major manufacturer of golf equipment. Management believes 
that Par’s market share could be increased with the introduction of a cutresistant, longer-lasting golf ball. Therefore, the research group at Par has 
been investigating a new golf ball coating designed to resist cuts and provide 
a more durable ball. The tests with the coating have been promising. One of 
the researchers voiced concern about the effect of the new coating on driving 
distances. Par would like the new cut-resistant ball to offer driving distances 
comparable to those of the current-model golf ball. To compare the driving 
distances for the two balls, 40 balls of both the new and current models were 
subjected to distance tests. The testing was performed with a mechanical 
hitting machine so that any difference between the mean distances for the 
two models could be attributed to a difference in the design.
The results of the tests, with distances measured to the nearest yard, are 
contained in the data set “Golf”. Prepare a Managerial Report

1. Formulate and present the rationale for a hypothesis test that par could 
use to compare the driving distances of the current and new golf balls   

2. Analyze the data to provide the hypothesis testing conclusion. What is the 
p-value for your test? What is your recommendation for Par Inc.?   

3. Provide descriptive statistical summaries of the data for each model   

4. What is the 95% confidence interval for the population mean of each 
model, and what is the 95% confidence interval for the difference 
between the means of the two population?   

5. Do you see a need for larger sample sizes and more testing with the golf 
balls? Discuss."   


\newpage

## Libraries/Packages
```{r}
library("readxl")
```

\newpage


## Set Working Directory
``` {r}
setwd("Z:/Projects for Github/Hypothesis Testing/GOLF BALL/Golf-Ball-Project")
getwd()
```

## Import Dataset
```{r}
mydata <- read_excel("Golf .xls")
```


## Import Dataset"
```{r}
mydata
```


\newpage
# Assumptions   
   
   
" The sample size of the data set is 40 from each model of golf ball. 
Central Limit Theorem states that irrespective of the shape of the original 
population, the sampling distribution of the mean will approach a normal 
distribution as the size of the sample increases and becomes large (>30). 
We also assume that the sample estimate will be reflective of the reality."






